### 2023-11-11 manuscript/manuscript.Rmd
Correct component removal statement
add reason for isotopic component removal

For each selected molecular formula, a component subgraph was constructed from the correlation network graph using all matching features, with features allowed across multiple components.
All components with a size of less than one and containing only isotopic features or adducts were removed.

>>>>

For each selected molecular formula, a component subgraph was constructed from the correlation network graph using all matching features, with features allowed across multiple components.
All components with a size of less than two were removed.
Isotopic *m/z* present without their non-isotopic counterparts are unlikely for molecular formulas below 1000 amu. Therefore, components containing only isotopic features or isotopic adducts were excluded.
